What is the Effect of X on Y?

### 2023-10-05 latex-slides/slides.tex
Update templates (no warnings!!)
Switch to .sty finally
Improved slide format:
- Improved footnote numbering
- New `\note{}` command for better table
- New `\bottomleft{}` command for putting beamer buttons
- IBM Plex mono font for `\ttfamily`
- No page numbering on table of contents

\documentclass[aspectratio=169,t]{beamer}
% \documentclass[aspectratio=43]{beamer}
\input{preamble.tex}

@@

\title{What is the Effect of X on Y?}
\date{\today}
\author{Kyle Butts}

\addbibresource{references.bib}

\begin{document}

% ------------------------------------------------------------------------------
\begin{frame}
\maketitle

@@

\begin{transitionframe}
  Transitioning Sentence
\end{transitionframe}

@@

        \item To include things in appendix, you must first label the slide and the appendix slide and then include a hyperlink:

        \vspace{5mm}
        \hyperlink{appendix1}{\beamergotobutton{Appendix}}
    \end{itemize}
\end{frame}

@@

\begin{frame}{Components}{Two Columns with Figure}
  \begin{columns}[T]
    \vspace{0pt}
    \begin{column}{.6\textwidth}
        \includegraphics[width=0.9\textwidth]{img/kanagawa.jpg}
    \end{column}
    \hfill
    \begin{column}{.4\textwidth}
        \begin{itemize}
            \item A point about the figure that is potentially important.
            \item Another point about the figure that is also potentially important.
        \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{Table}
  \begin{columns}[T]
    \begin{column}{.6\textwidth}
      % Adjust Font Size to make table fit   
      \begin{table}[!htbp]
        % \caption{Regression Results}

        \begin{adjustbox}{max width = \textwidth, width = 0.8 \textwidth, center}
            \begin{threeparttable}
                \begin{tabular}{@{} l *{2}{r} @{}} 
                    \toprule
                    & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
                    \cline{2-3} \\
                    & (1) & (2)\\ 
                    \midrule

@@

                \end{tabular} 
                % Notes 
                \begin{tablenotes}
                    \item \textit{Notes.} $^{*} p<0.1$; $^{**} p<0.05$; $^{***} p<0.01$.
                \end{tablenotes}
            \end{threeparttable}
        \end{adjustbox}
      \end{table}
    \end{column}
    \hfill
    \begin{column}{.4\textwidth}
        \begin{itemize}
            \item Use \texttt{\textbackslash marktopleft\{name\}} and \texttt{\textbackslash markbottomright\{name\}} within the table to create box.
            \item Using \texttt{\textbackslash only} or \texttt{\textbackslash on} lets you conditionally display box
        \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

% ------------------------------------------------------------------------------
\begin{frame}[allowframebreaks]{References}
    \printbibliography
\end{frame}
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\appendix
% ------------------------------------------------------------------------------

\begin{frame}{Appendix Slide}{\hyperlink{main1}{\beamergotobutton{Back to Main}}}\label{appendix1}
  \begin{table}
    \caption{Summary Statistics}
    \label{appendix_summ_stat}
    \begin{adjustbox}{max width = \textwidth, width = 0.7\textwidth, center}
      \begin{threeparttable}
        \begin{tabular}{@{} lccccccc @{}} 
          \toprule
          Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
          \hline \\[-1.8ex] 
          rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
          complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
          privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
          learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
          raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
          \bottomrule
        \end{tabular}

        \begin{tablenotes}
            \item \textit{Notes.} Using R base dataframe attitude.
        \end{tablenotes}
      \end{threeparttable}
    \end{adjustbox}
  \end{table}
\end{frame}

>>>>

\documentclass[aspectratio=169,t,11pt]{beamer}
% \documentclass[aspectratio=43,t,11pt]{beamer}
\usepackage{slides,math}

@@

\title{What is the Effect of X on Y?}
\date{\today}
\author{Kyle Butts}
\addbibresource{references.bib}
\begin{document}

% ------------------------------------------------------------------------------
\begin{frame}[noframenumbering,plain]
\maketitle

@@

@@

    \item To include things in appendix, you must first label the slide and the appendix slide and then include a hyperlink. The command \texttt{\textbackslash bottomleft} will position in the bottom left corner nicely
  \end{itemize}

  \bottomleft{\hyperlink{appendix1}{\beamergotobutton{Appendix}}}
\end{frame}

@@

\begin{frame}{Components}{Two Columns with Figure}
  \begin{columns}[T]
  \vspace{0pt}
  \begin{column}{.5\textwidth}
    \includegraphics[width=\textwidth]{img/kanagawa.jpg}
  \end{column}
  \hfill
  \begin{column}{.48\textwidth}
    \begin{itemize}
    \item A point about the figure that is potentially important.
    \item Another point about the figure that is also potentially important.
    \end{itemize}
  \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{Table}
  \begin{columns}[T]
  \begin{column}{.4\textwidth}
    \begin{adjustbox}{max width = \textwidth, center}
      \begin{tabular}{@{} l *{2}{r} @{}} 
        \toprule
        & (1) & (2)\\ 
        \midrule

@@

      \end{tabular}   
    \end{adjustbox}

    \note{$^{*} p<0.1$; $^{**} p<0.05$; $^{***} p<0.01$.}
  \end{column}
  \hfill
  \begin{column}{.5\textwidth}
    \begin{itemize}
      \item Use \texttt{\textbackslash marktopleft\{name\}} and \texttt{\textbackslash markbottomright\{name\}} within the table to create box.
      \item Using \texttt{\textbackslash only} or \texttt{\textbackslash on} lets you conditionally display box
    \end{itemize}
  \end{column}
  \end{columns}
\end{frame}

@@

% ------------------------------------------------------------------------------
\begin{frame}[allowframebreaks,noframenumbering]{References}
  \thispagestyle{empty}
  \printbibliography
\end{frame}
\appendix
% ------------------------------------------------------------------------------

\begin{frame}{Appendix Slide}{Summary Slides}\label{appendix1}
  \begin{table}[t]
    % \caption{Summary Statistics}\label{tab:summary_stats}
    \begin{adjustbox}{width = 0.8\textwidth}
      \begin{tabular}{@{} lccccccc @{}} 
        \toprule
        Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
        \hline \\[-1.8ex] 
        rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
        complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
        privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
        learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
        raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
        \bottomrule
      \end{tabular} 
    \end{adjustbox}

    \note{0.8\textwidth}{Using R base dataframe \texttt{attitude}. R base dataframe attitude. R base dataframe attitude.}
  \end{table}

  \bottomleft{\hyperlink{main1}{\beamerreturnbutton{Back}}}
  % \bottomright{\hyperlink{main1}{\beamerreturnbutton{Back}}}
\end{frame}
